BECKY:\\Bayesian Estimation of Coevolutionary KrYteria

### 2013-07-17 paper/article.tex
Minor progress; mostly of TODO/reminder nature

% !BIB TS-program = biber
\documentclass[12pt,letterpaper]{article}

@@

@@

A likelihood implementation has many advantages \cite{Charleston:2009}.

>>>>

% !TEX TS-program = pdflatex
% !BIB TS-program = biber
\documentclass[12pt,letterpaper]{article}

@@

It is important to note that the host-symbiont [reconciliation] problem is largely similar to the gene tree--species tree [reconciliation] problem. Accordingly, it is worth comparing these

\textcite{Akerborg:2009} compare [reconciliation] methods to the evolution of methods for phylogenetic evidence, highlighting the shift to the probabilistic, and in particular, Bayesian approach.

@@

A likelihood implementation has many advantages \parencite{Charleston:2009}.
